---
title: "Wisconsin State Frisbee Tournament Results"
output: html_document
date: "2024-08-17"
editor_options: 
  chunk_output_type: console
---


Authorization
```{r}
library(googlesheets4)

# De-authorize any existing token
googlesheets4::gs4_deauth()

# Explicitly authorize with the appropriate scope
googlesheets4::gs4_auth(
  scopes = "https://www.googleapis.com/auth/spreadsheets.readonly"
)
```

Read the sheet
```{r}
url <- "https://docs.google.com/spreadsheets/d/1NNZ0dWsWdY8BM3R6KGCDZAMMH_O_Xikl7_PB1SVsLSY/edit#gid=0"
Results.df <- googlesheets4::read_sheet(url,
                                        range = "A1:U",
                                        na = "NA",
                                        col_types = "cncccccccccccccnnnnnc"
                                        )
```

```{r}
names(Results.df)
```


Bests
```{r}
div <- "Open"
eve <- "Accuracy"
Xp <- Results.df |>
  dplyr::filter(Event == eve, Division == div) |>
  dplyr::select(Year, Event, Division, Place, Name = "Player 1", 
                Measurement = "Scores 1")
Xf <- Results.df |>
  dplyr::filter(Event == eve, Division == div) |>
  dplyr::select(Year, Event, Division, Place, Name = "Player 1", 
                Measurement = "Scores 2")

Xf2 <- Results.df |>
  dplyr::filter(Event == eve, Division == div) |>
  dplyr::select(Year, Event, Division, Place, Name = "Player 1", 
                Measurement = "Scores 3")
X <- rbind(Xp, Xf, Xf2)
X |> 
  dplyr::arrange(desc(Measurement)) |>
  print(n = 30)
```

Number of 1st place finishes
```{r}
div <- "Open"
eve <- "Accuracy"
Results.df |>
  dplyr::filter(Event == eve, Division == div, Place == "1st") |>
  dplyr::select(Tournament, Year, Name = "Player 1") |>
  dplyr::group_by(Name) |>
  dplyr::summarise(
                   Event = eve,
                   Division = div,
                   Firsts = dplyr::n()
                   ) |>
  dplyr::arrange(desc(Firsts))
```

Number of podium finishes all events
```{r}
div <- "Open"
P1 <- Results.df |>
  dplyr::filter(Division == div) |>
  dplyr::select(Tournament, Year, Name = "Player 1") |>
  dplyr::filter(Name != "") |>
  dplyr::group_by(Name) |>
  dplyr::summarise(
                   Division = div,
                   Podiums = dplyr::n()
                   ) |>
  dplyr::arrange(desc(Podiums))
P2 <- Results.df |>
  dplyr::filter(Division == div) |>
  dplyr::select(Tournament, Year, Name = "Player 2") |>
  dplyr::filter(Name != "") |>
  dplyr::group_by(Name) |>
  dplyr::summarise(
                   Division = div,
                   Podiums = dplyr::n()
                   ) |>
  dplyr::arrange(desc(Podiums))
P3 <- Results.df |>
  dplyr::filter(Division == div) |>
  dplyr::select(Tournament, Year, Name = "Player 3") |>
  dplyr::filter(Name != "") |>
  dplyr::group_by(Name) |>
  dplyr::summarise(
                   Division = div,
                   Podiums = dplyr::n()
                   ) |>
  dplyr::arrange(desc(Podiums))

P <- dplyr::full_join(P1, P2, by = "Name")
P <- dplyr::full_join(P, P3, by = "Name")

P <- P |>
  dplyr::mutate_all(~ ifelse(is.na(.), 0, .))

P$Podiums <- P$Podiums.x + P$Podiums.y + P$Podiums

P |> 
  dplyr::select(Name, Podiums) |>
  dplyr::arrange(desc(Podiums)) |>
  print(n = 25)
```

Individual bests
```{r}
person <- "Andrew Lemann"

events <- c("Accuracy", "Distance", "SCF")
Results.df |> 
  dplyr::select(Player = "Player 1", Year, Location, Event,
                Measurement1 = "Scores 1",
                Measurement2 = "Scores 2",
                Measurement3 = "Scores 3") |>
  dplyr::filter(Player == person) |>
  dplyr::filter(Event %in% events) |>
  tidyr::pivot_longer(cols = c("Measurement1", "Measurement2", "Measurement3"),
                      names_to = "Which",
                      values_to = "Measurement") |>  
  dplyr::group_by(Event) |>
  dplyr::slice_max(Measurement) |>
  dplyr::select(Player, Year, Location, Event, Measurement)

events <- c("Golf", "Discathon")
Results.df |> 
  dplyr::select(Year, Event, Location, Player = "Player 1", 
                Measurement1 = "Scores 1",
                Measurement2 = "Scores 2",
                Measurement3 = "Scores 3") |>
  dplyr::filter(Player == person) |>
  dplyr::filter(Event %in% events) |>
  tidyr::pivot_longer(cols = c("Measurement1", "Measurement2"),
                      names_to = "Which",
                      values_to = "Measurement") |>
  dplyr::group_by(Event) |>
  dplyr::slice_min(Measurement) |>
  dplyr::select(Player, Year, Location, Event, Measurement)

```

Create a SQL database
```{r}
# Install necessary packages if not already installed
install.packages("googlesheets4")
install.packages("DBI")
install.packages("RSQLite")
```

```{r}
library(DBI)
library(RSQLite)

# Connect to SQLite database (or create it if it doesn't exist)
con <- dbConnect(RSQLite::SQLite(), "data/WI_State_Results.db")

# View the data to ensure it has loaded correctly
print(Results.df)
```

```{r}
# Write data to the SQL database; this creates a new table named 'your_table'
dbWriteTable(con, "db_structure", Results.df, overwrite = TRUE)

# Verify the data is in the database
dbListTables(con)
dbReadTable(con, "db_structure")

# Close the database connection
dbDisconnect(con)
```

This approach can be adapted to other SQL databases like MySQL or PostgreSQL by changing the connection details (`dbConnect()`).

Ensure that your Google Sheets API credentials have the correct permissions if you run into access issues.


